Validity of a model for a cantilever two-dimensional beam

### 2024-04-07 files/Chapter1/1DModel.tex
appendix
review exam report

    \subsection{Equations of motion and constitutive equations}\label{subsec:equationsofmotion+constitutiveequation}
    In this section we introduce the Timoshenko beam theory for the transverse vibration of a uniform beam.
    For a reference of the model~\cite{Inm94}, and~\cite{Fu65} were used.\\

@@

    \subsubsection*{Equations of motion}\label{sssec:1D_Model:EquationOfMotion}
    \begin{align}
        \rho A \partial_t^2 w &=& \partial_x V + Q, \label{eq:1D_Model:EquationOfMotion1}\\
        \rho I\partial_t^2 \phi  &=& V + \partial_x M. \label{eq:1D_Model:EquationOfMotion2}
    \end{align}\label{sym:A}\label{sym:V}\label{sym:Iinertia}\label{sym:M}\label{sym:phiT}
    In~\eqref{eq:1D_Model:EquationOfMotion1} and \eqref{eq:1D_Model:EquationOfMotion2} $\rho$ denotes the density, $A$ is the area of a cross section, $I$ is the area moment of inertia, $M$ is the moment, $V$ is the shear force and $Q$ is an external force acting on the beam.

@@

    \subsubsection*{Dimensionless form}\label{sssec:1D_Model:DimensionlessForm}
    As mentioned in subsection \ref{ssec:3D_Model:DimensionlessForm}, the same dimensionless scaling is used for all the models in this dissertation.\\

@@

    Choose $t_0$ the same as in subsection \ref{ssec:3D_Model:DimensionlessForm}, i.e. \[t_0 = \ell\sqrt{\frac{\rho}{G\kappa^2}}.\]

@@

    Interestingly, it turns out that
    \begin{eqnarray*}
        \frac{\beta}{\alpha} & = & \gamma
    \end{eqnarray*} where $\gamma$ is the dimensionless parameter defined in subsection \ref{ssec:3D_Model:DimensionlessForm}.\\

    \textbf{Remark} Recall that in subsection \ref{ssec:3D_Model:DimensionlessForm} the constant $G\kappa^2$ was used for the scaling of the stresses.

>>>>

    \subsection{Equations of motion and constitutive equations}\label{subsec:equationsofmotion+constitutiveequation}
    In this section we introduce the Timoshenko beam theory for the transverse vibration of a uniform beam.
    For a reference of the model~\cite{Timo21}, and~\cite{Fung65} were used.\\

@@

    \subsubsection*{Equations of motion}\label{sssec:1D_Model:EquationOfMotion}
    \begin{eqnarray}
        \rho A \partial_t^2 w &=& \partial_x V + Q, \label{eq:1D_Model:EquationOfMotion1}\\
        \rho I\partial_t^2 \phi  &=& V + \partial_x M. \label{eq:1D_Model:EquationOfMotion2}
    \end{eqnarray}\label{sym:A}\label{sym:V}\label{sym:Iinertia}\label{sym:M}\label{sym:phiT}
    In~\eqref{eq:1D_Model:EquationOfMotion1} and \eqref{eq:1D_Model:EquationOfMotion2} $\rho$ denotes the density, $A$ is the area of a cross section, $I$ is the area moment of inertia, $M$ is the moment, $V$ is the shear force and $Q$ is an external force acting on the beam.

@@

    \subsubsection*{Dimensionless form}\label{sssec:1D_Model:DimensionlessForm}
    As mentioned in Subsection \ref{ssec:3D_Model:DimensionlessForm}, the same dimensionless scaling is used for all the models in this dissertation.\\

@@

    Choose $t_0$ the same as in Subsection \ref{ssec:3D_Model:DimensionlessForm}, i.e. \[t_0 = \ell\sqrt{\frac{\rho}{G\kappa^2}}.\]

@@

    Interestingly, it turns out that
    \begin{eqnarray*}
        \frac{\beta}{\alpha} & = & \gamma
    \end{eqnarray*} where $\gamma$ is the dimensionless parameter defined in Subsection \ref{ssec:3D_Model:DimensionlessForm}.\\

    \textbf{Remark} Recall that in Subsection \ref{ssec:3D_Model:DimensionlessForm} the constant $G\kappa^2$ was used for the scaling of the stresses.

### 2024-04-07 files/Chapter1/2DModel.tex
review exam report

\subsubsection{Problem 2D-1}\label{sssec:2D_Model:Problem2D1}
Find a vector valued function $u$, satisfying equations \eqref{eq:2D_Model:EM} to \eqref{eq:2D_Model:CE} and the boundary conditions:\\

Boundary Conditions:\\
\begin{eqnarray*}
	u & = & 0 \quad \textrm{ on } \Sigma,\\
	Tn & = & 0 \quad \textrm{ on } \Gamma.
\end{eqnarray*} with $n$ the outward unit normal.

\subsection{Variational form}\label{ssec:2D_Model:VariationalForm}
The steps to derive the variational form is almost identical to the case of the three-dimensional case. Therefore it is not shown again and only the differences are discussed. \\

@@

 Applications are continued in Chapter 5 and 6. In Chapter 5, the finite element analysis is applied to a cantilever beam to solve the eigenvalue problem. In Chapter 6, a cantilever beam in used in the comparison of our linear models.

>>>>

\subsubsection{Problem 2D-1}\label{sssec:2D_Model:Problem2D1}
Find a vector valued function $u$, satisfying equations \eqref{eq:2D_Model:EM} to \eqref{eq:2D_Model:CE} and the boundary conditions:

\begin{eqnarray*}
	u & = & 0 \quad \textrm{ on } \Sigma,\\
	Tn & = & 0 \quad \textrm{ on } \Gamma.
\end{eqnarray*} with $n$ the outward unit normal.

\subsection{Variational form}\label{ssec:2D_Model:VariationalForm}
The steps to derive the variational form is almost identical to the three-dimensional case. Therefore it is not shown again and only the differences are discussed. \\

@@

 Applications are continued in Chapter 5 and 6. In Chapter 5, the finite element method is applied to a cantilever beam to solve the eigenvalue problem. In Chapter 6, a cantilever beam in used in the comparison of our linear models.

### 2024-04-07 files/Chapter1/PlateModel.tex
review exam report

	Let $w$ represent the displacement of the plate body and $\psi$ the angle between the material line and a line perpendicular to the plate. In the spherical coordinate form, the angle can easily be calculated for the directions of $\bar{e}_1$ and $\bar{e}_2$, i.e.
	\begin{eqnarray*}
		\psi_1 & = & \frac{q}{r} \bar{e}_r \cdot \bar{e}_1, \\
		\psi_2 & = & \frac{q}{r} \bar{e}_r \cdot \bar{e}_2.
	\end{eqnarray*}
	Define
	\begin{eqnarray*}
		{\psi} = \langle \psi_1 \  \psi_2\rangle = \langle \sin\phi \cos \theta \ \ \sin\phi \sin \theta\rangle.
	\end{eqnarray*}

	The plate model in consideration is restricted to a linear model. Therefore $\sin\phi$ can be approximated by $\phi$ such that
	\begin{eqnarray*}
		{\psi} = \langle \psi_1 \  \psi_2\rangle = \langle \phi \cos \theta \ \ \phi \sin \theta \rangle.
	\end{eqnarray*}

@@

	\subsection{Equations of Motion and Constitutive Equations}\label{ssec:P_Model:EquationsOfMotion+ConstitutiveEquation}
	Consider a Reissner-Mindlin plate with reference configuration $\Omega \in R^2$. Let $u \in \Omega$ define the transverse motion of the plate model and $\psi = \langle \psi_1 \ \psi_2 \rangle$ the angle between the material line and a line perpendicular to the plate.

	\subsubsection*{Equations of Motion}\label{sssec:P_Model:EquationsOfMotion}
	\begin{eqnarray}
		\rho h \partial_t^2 w & = & \textrm{div} \mathbf{Q} + q \label{eq:P_Model:EM1}\\
		\rho I \partial_t^2 {\psi} & = & \textrm{div} M - Q \label{P2}\label{eq:P_Model:EM1}
	\end{eqnarray} \label{sym:bfQ}
	In these equations $\rho$ denotes the density of the plate, $\displaystyle I = \frac{h^3}{12}$ the length moment of inertia, $M$ the moment density and $Q$ the shear force density. The parameter $q$ is an external force acting on the plate. The moment density is defined as

@@

	\subsubsection{Remark}
	Similar to the model in section \ref{ssec:3D_Model:DimensionlessForm}, the constant $G$ is introduced to allow for the comparison of models in later chapters. It will also be required that $\kappa$ is the same for the beam and plate models.

@@

	Some commonly used boundary (or edge) conditions are:\\

@@

	\subsection{Model Problems}\label{ssec:P_Model:ModelProblems}
	Let $\Omega \subset R^2$ denote reference configuration of the plate model. Following \cite{Wu05}, $\Omega$ is a rectangle.\\

@@

	\subsubsection{Problem P-1}\label{sssec:P_Model:ProblemP1}
	Consider a cantilever plate model. In this configuration, the plate is clamped at one edge and free hanging at the rest of the boundary. With out loss of generality, assume that the plate is clamped on the edge $\Sigma_0$.\\

	Find functions $w$ and $\psi$ satisfying equations \eqref{eq:P_Model:EM1D} to \eqref{eq:P_Model:CE4D_chap1}, the boundary conditions.\\

	Boundary Conditions\\
	\[w = 0,  \ \textrm{ and } \ \psi = \bar{0} \ \textrm{ on } \Sigma_0.\]
	\[Mn\cdot n = 0,\ \ \ Mn\cdot \tau = 0, \ \textrm{ and } \ \mathbf{Q} \cdot n =0 \ \textrm{ on } \partial\Omega\setminus\Sigma_0.\]
	with $\tau$ a unit vector perpendicular to $n$.\\

	\subsubsection{Problem P-2}\label{sssec:P_Model:ProblemP2}
	Consider a plate model that is rigidly clamped on $\partial \Omega$. Find functions $w$ and $\psi$ satisfying equations \eqref{eq:P_Model:EM1D} to \eqref{eq:P_Model:CE4D_chap1}, the boundary conditions.\\

	Boundary Conditions\\
	\[w = 0,  \ \textrm{ and } \ \psi = \bar{0} \ \textrm{ on } \partial \Omega.\]

	\subsection{Variational Form}\label{ssec:P_Model:VariationalForm}
	Let $v \in C_2^1[0,1]$ and $w \in C^1[0,1] \times C^1[0,1]$ such that $w$ is a vector valued function. Multiplication these functions to \eqref{eq:P_Model:EM1D} and \eqref{eq:P_Model:EM2D} yields:
	\begin{eqnarray*}
		\int_\Omega h \partial_t^2 w v \ dA & = & \int_\Omega \textrm{div} (\mathbf{Q}) v \ dA + \int_\Omega q v \ dA\\
		\int_\Omega I \partial_t^2 \psi \cdot \phi \ dA & = & \int_\Omega \textrm{div} (M) \cdot \phi \ dA - \int_\Omega Q \cdot \phi \ dA
	\end{eqnarray*}

	Following from Green's Formulas, similar to section \ref{ssec:3D_Model:VariationalForm}, 
	\begin{eqnarray*}
		\int_\Omega \textrm{div}(\mathbf{Q}) v \ dA & = & - \int_\Omega \mathbf{Q} \cdot \nabla v \ dA + \int_{\partial\Omega} (Q\cdot n)v ds,\\
		\int_\Omega \textrm{div}(M) \cdot \phi \ dA & = & - \int_\Omega \textrm{Tr} (M \Phi) \ dA + \int_{\partial\Omega} M n \cdot \phi ds.
	\end{eqnarray*}
	$\textrm{Tr} (M \Phi)$ is the trace of the matrix $M \Phi$, $n$ is the normal vector to $\Omega$, and 
	\begin{eqnarray*}
		\Phi = 
		\begin{bmatrix}
			\partial_1\phi_1 & \partial_2\phi_1\\
			\partial_1\phi_2 & \partial_2\phi_2
		\end{bmatrix}.
	\end{eqnarray*}

	The variational form can be given as
	\begin{align}
		\int_\Omega h \partial_t^2 w v \ dA & = & - \int_\Omega Q \cdot \nabla v \ dA + \int_\Omega q v \ dA + \int_{\partial\Omega} (Q\cdot n)v ds, \label{P1}\\
		\int_\Omega I \partial_t^2 \psi \cdot \phi \ dA & = & - \int_\Omega \textrm{Tr} (M \Phi) \ dA - \int_\Omega Q \cdot \phi \ dA + \int_{\partial\Omega} M n \cdot \phi ds. \label{P2}
	\end{align}

@@

 Applications are continued in Chapter 5 and 6. In Chapter 5, the finite element analysis is applied to a cantilever plate to solve the eigenvalue problem. In Chapter 6, a cantilever plate in used in the comparison of our linear models.
\end{document}

>>>>

	Let $w$ represent the displacement of the plate body and $\psi$ the angle between the material line and a line perpendicular to the plate. In the spherical coordinate form, the angle can easily be calculated for the directions of $\bar{e}_1$ and $\bar{e}_2$, i.e.
	\begin{eqnarray*}
		\psi_1 & = & \frac{q}{r} \bar{e}_r \cdot \bar{e}_1, \\
		\psi_2 & = & \frac{q}{r} \bar{e}_r \cdot \bar{e}_2.
	\end{eqnarray*}
	Define
	\begin{eqnarray*}
		{\psi} = \langle \psi_1, \ \psi_2\rangle = \langle \sin\phi \cos \theta, \ \sin\phi \sin \theta\rangle.
	\end{eqnarray*}

	The plate model in consideration is restricted to a linear model. Therefore $\sin\phi$ can be approximated by $\phi$ such that
	\begin{eqnarray*}
		{\psi} = \langle \psi_1, \  \psi_2\rangle = \langle \phi \cos \theta, \ \phi \sin \theta \rangle.
	\end{eqnarray*}

@@

	\subsection{Equations of Motion and Constitutive Equations}\label{ssec:P_Model:EquationsOfMotion+ConstitutiveEquation}
	Consider a Reissner-Mindlin plate with reference configuration $\Omega \in R^2$. Let $u \in \Omega$ define the transverse motion of the plate model and $\psi = \langle \psi_1, \ \psi_2 \rangle$ the angle between the material line and a line perpendicular to the plate.

	\subsubsection*{Equations of Motion}\label{sssec:P_Model:EquationsOfMotion}
	\begin{eqnarray}
		\rho h \partial_t^2 w & = & \textrm{div} \mathbf{Q} + q \label{eq:P_Model:EM1}\\
		\rho I \partial_t^2 {\psi} & = & \textrm{div} M - Q \label{P2}\label{eq:P_Model:EM1}
	\end{eqnarray} \label{sym:bfQ}
	In these equations $\rho$ denotes the density of the plate, $\displaystyle I = \frac{h^3}{12}$ the length moment of inertia, $M$ the moment density and $Q$ the shear force density. The parameter $q$ is an external force acting on the plate. $\mathbf{Q}$ is defined as part of the constitutive equations below. The moment density is defined as

@@

	\subsubsection{Remark}
	Similar to the model in Section \ref{ssec:3D_Model:DimensionlessForm}, the constant $G$ is introduced to allow for the comparison of models in later chapters. It will also be required that $\kappa$ is the same for the beam and plate models.

	For convienience, the original notation is used for the dimensionless form.

@@

	Some commonly used boundary (or edge) conditions are:

@@

	\subsection{Model Problems}\label{ssec:P_Model:ModelProblems}
	Let $\Omega \subset R^2$ denote reference configuration of the plate model. Following \cite{Wu06}, $\Omega$ is a rectangle.

@@

	\subsubsection{Problem P-1}\label{sssec:P_Model:ProblemP1}
	Consider a cantilever plate model. In this configuration, the plate is clamped at one edge and free hanging at the rest of the boundary. Without loss of generality, assume that the plate is clamped on the edge $\Sigma_0$.

	Find functions $w$ and $\psi$ satisfying equations \eqref{eq:P_Model:EM1D} to \eqref{eq:P_Model:CE4D_chap1} and the boundary conditions:

	\[w = 0,  \ \textrm{ and } \ \psi = \bar{0} \ \textrm{ on } \Sigma_0.\]
	\[Mn\cdot n = 0,\ \ \ Mn\cdot \tau = 0, \ \textrm{ and } \ \mathbf{Q} \cdot n =0 \ \textrm{ on } \partial\Omega\setminus\Sigma_0.\]
	with $\tau$ a unit vector perpendicular to $n$.

	\subsubsection{Problem P-2}\label{sssec:P_Model:ProblemP2}
	Consider a plate model that is rigidly clamped on $\partial \Omega$. Find functions $w$ and $\psi$ satisfying equations \eqref{eq:P_Model:EM1D} to \eqref{eq:P_Model:CE4D_chap1} and the boundary conditions:\\

	\[w = 0,  \ \textrm{ and } \ \psi = \bar{0} \ \textrm{ on } \partial \Omega.\]

	\subsection{Variational Form}\label{ssec:P_Model:VariationalForm}
	Let $v \in C_2^1[0,1]$ and $w \in C^1[0,1] \times C^1[0,1]$ such that $w$ is a vector valued function. Multiplication these artitrary functions to \eqref{eq:P_Model:EM1D} and \eqref{eq:P_Model:EM2D_chap1} yields:
	\begin{eqnarray*}
		\int_\Omega h \partial_t^2 w v \ dA & = & \int_\Omega \textrm{div} (\mathbf{Q}) v \ dA + \int_\Omega q v \ dA\\
		\int_\Omega I \partial_t^2 \psi \cdot \phi \ dA & = & \int_\Omega \textrm{div} (M) \cdot \phi \ dA - \int_\Omega Q \cdot \phi \ dA
	\end{eqnarray*}

	Following from Green's Formulas, similar to Section \ref{ssec:3D_Model:VariationalForm}, 
	\begin{eqnarray*}
		\int_\Omega \textrm{div}(\mathbf{Q}) v \ dA & = & - \int_\Omega \mathbf{Q} \cdot \nabla v \ dA + \int_{\partial\Omega} (Q\cdot n)v ds,\\
		\int_\Omega \textrm{div}(M) \cdot \phi \ dA & = & - \int_\Omega \textrm{Tr} (M \Phi) \ dA + \int_{\partial\Omega} M n \cdot \phi ds.
	\end{eqnarray*}
	$\textrm{Tr} (M \Phi)$ is the trace of the matrix $M \Phi$, $n$ is the normal vector to $\Omega$, and 
	\begin{eqnarray*}
		\Phi = 
		\begin{bmatrix}
			\partial_1\phi_1 & \partial_2\phi_1\\
			\partial_1\phi_2 & \partial_2\phi_2
		\end{bmatrix}.
	\end{eqnarray*}

	The variational form is given as
	\begin{align}
		\int_\Omega h \partial_t^2 w v \ dA & = & - \int_\Omega Q \cdot \nabla v \ dA + \int_\Omega q v \ dA + \int_{\partial\Omega} (Q\cdot n)v ds, \label{P1}\\
		\int_\Omega I \partial_t^2 \psi \cdot \phi \ dA & = & - \int_\Omega \textrm{Tr} (M \Phi) \ dA - \int_\Omega Q \cdot \phi \ dA + \int_{\partial\Omega} M n \cdot \phi ds. \label{P2}
	\end{align}

@@

 Applications are continued in Chapter 5 and 6. In Chapter 5, the finite element method is applied to a cantilever plate to solve the eigenvalue problem. In Chapter 6, a cantilever plate in used in the comparison of the linear models.
\end{document}
